\documentclass[letterpaper,11pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[compact]{titlesec}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}
\pagenumbering{gobble}

\begin{document}

{\LARGE \textbf{Abhinav Bhatia}}\\
Ph.D. candidate at University of Massachusetts Amherst \\
\href{mailto:abhinavbhati@cs.umass.edu}{abhinavbhati@cs.umass.edu} $|$ \href{https://abhinavbhatia.me}{abhinavbhatia.me}

{\small Last updated: March 26, 2026. Latest CV available at \href{https://abhinavbhatia.me/#cv}{abhinavbhatia.me/\#cv}}

\section*{Interests}
Reinforcement Learning, Inverse RL, Offline RL, Real-time Planning, AI Safety, Autonomous Vehicles, Robotics, LLM-assisted decision making

\section*{Education}
\textbf{University of Massachusetts Amherst} \hfill 3.95/4\\
MS/Ph.D. in Computer Science, advised by Prof. Shlomo Zilberstein \hfill Fall 2019 -- Present

\textbf{Birla Institute of Technology and Science (BITS) - Pilani, Pilani Campus} \hfill 9.27/10\\
B.E. (Hons.) in Computer Science \hfill Aug. 2011 -- May 2015

\section*{AV Relevant Research Projects}

\textbf{Safe Runtime Personalization of AV Driving Behavior (Ongoing PhD project)}
\vspace{-1em}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Developed a meta-reasoning framework with deep RL that enables users to customize driving personality at runtime through multiple preference variables (resulting in millions of combinations) while provably guaranteeing safety even for previously untested preference vectors.
  \item Addresses core AV adoption and safety challenges at scale by moving beyond fixed preset policies.
  \item The approach is applicable to any robotic or AI assistant.
\end{itemize}
\vspace{-0.5em}
\textbf{Awesim: High-Fidelity 2D Autonomous Vehicle Simulator}
\vspace{-1em}
\begin{itemize}
\setlength\itemsep{0em}
  \item Designed and implemented a full-stack \href{https://github.com/bhatiaabhinav/Awesim}{simulator} from scratch in pure C, enabling point-to-point driving simulation in seconds.
  \item Includes a city map, NPC traffic, real-time path planning, and a lidar and multi-camera vision stack; supports ego control with deep RL through Python bindings or with lightweight deep-RL implemented in C.
\end{itemize}

\section*{Experience}
\textbf{Applied Sciences Intern} \hfill June 2024 -- August 2024\\
Xbox Game Studios, Microsoft, Redmond, WA, USA
\vspace{-1em}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Multi-task inverse and offline reinforcement learning for language conditioned automated gameplay.
\end{itemize}
\vspace{-0.5em}
\textbf{Research Engineer} \hfill June 2017 -- July 2019\\
School of Computing and Information Sciences, Singapore Management University, Singapore
\vspace{-1em}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Supervised by Prof. Pradeep Varakantham and Prof. Akshat Kumar.
  \item Worked on optimizing constrained resource allocation at city scale with semireal datasets using deep reinforcement learning.
\end{itemize}
\vspace{-0.5em}
\textbf{Software Engineer} \hfill August 2015 -- June 2017\\
WalmartLabs, Bengaluru, India
\vspace{-1em}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Was part of the \emph{Operations, Analytics \& Research} team in the supply-chain division of Walmart eCommerce.
  \item Developed an Elasticsearch-based distributed database for data analysis.
  \item Developed a deep-learning-based system for anomaly detection in large, live incoming data streams.
\end{itemize}
\vspace{-0.5em}
\textbf{Software Development Engineering Intern} \hfill January 2015 -- June 2015\\
Amazon, Bengaluru, India
\vspace{-1em}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Worked on offline experience for Prime Video.
  \item Worked on optimizing content load time for Prime Video on Kindle tablets.
\end{itemize}

\section*{Publications}
\textbf{Abhinav Bhatia}, Samer B. Nashed and Shlomo Zilberstein. ``RL$^3$: Boosting Meta Reinforcement Learning via RL inside RL$^2$". In \textit{NeurIPS Workshop on Generalization in Planning (NeurIPS GenPlan 2023)} and \textit{Reinforcement Learning Conference (RLC 2025)}.

Samer B. Nashed, Justin Svegliato, \textbf{Abhinav Bhatia}, Stuart Russell and Shlomo Zilberstein (2022). ``Selecting the partial state abstractions of MDPs: A metareasoning approach with deep reinforcement learning". In \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2022)}.

\textbf{Abhinav Bhatia}, Justin Svegliato, Samer B. Nashed and Shlomo Zilberstein. ``Tuning the Hyperparameters of Anytime Planning: A Metareasoning Approach with Deep Reinforcement Learning". In \textit{Proceedings of the International Conference on Automated Planning and Scheduling (ICAPS 2022)}.

\textbf{Abhinav Bhatia}, Philip S. Thomas, and Shlomo Zilberstein. ``Adaptive Rollout Length for Model-Based RL Using Model-Free Deep RL". In \textit{(ArXiv 2022)}.

\textbf{Abhinav Bhatia}, Justin Svegliato and Shlomo Zilberstein. ``On the Benefits of Randomly Adjusting Anytime Weighted A*". In \textit{Proceedings of the International Symposium on Combinatorial Search (SoCS 2021)}.

\textbf{Abhinav Bhatia}, Pradeep Varakantham and Akshat Kumar. ``Resource Constrained Deep Reinforcement Learning". In \textit{Proceedings of the International Conference on Automated Planning and Scheduling (ICAPS 2019)}.

\section*{Relevant Ph.D. Coursework}
Artificial Intelligence, Reinforcement Learning, Robotics, Advanced Robot Dynamics \& Control, Machine Learning, Neural Networks, Advanced Algorithms

\section*{Programming Skills}
\textbf{Languages}: Experienced in C, Python, Julia. Familiar with C++ (built full game in undergrad)\\
\textbf{Frameworks}: PyTorch, OpenAI Gym, Isaac Sim, Tensorflow, CPLEX, Unity3D

\section*{Teaching \& Service}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Dissertation Writing Fellowship Award, UMass Amherst, Spring 2026.
  \item Organizing committee member, AAAI 2025 GenPlan workshop.
  \item Program Committee member: IJCAI 2026, 2025, 2024; NeurIPS GenPlan 2023; AAAI 2023.
  \item Paper reviewer, JMLR, 2023; AIJ 2021.
  \item Teaching Assistant, CS383 Artificial Intelligence, UMass Amherst (Fall 2022).
\end{itemize}

\section*{Misc.}
\begin{itemize}
    \setlength\itemsep{0em}
  \item Conceptualized, developed and organized AI bot-making competition for a video game (IEEE BITS-Pilani chapter, 2014).
  \item 1st Prize - PC 3D Gesture Interface using Kinect (BITS-Pilani Tech Festival 2014).
  \item Offered Kishore Vaigyanik Protsahan Yojana (KVPY) Fellowship, Govt. of India (2010).
\end{itemize}
% \vspace{-1em}
\section*{Links}
\textbf{Webpage}: \href{https://abhinavbhatia.me}{https://abhinavbhatia.me}\\
\textbf{GitHub}: \href{https://github.com/bhatiaabhinav}{https://github.com/bhatiaabhinav}\\
\textbf{Google Scholar}: \href{https://scholar.google.com/citations?user=Y53CNrIAAAAJ\&hl}{https://scholar.google.com/citations?user=Y53CNrIAAAAJ\&hl}

\end{document}
