%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{enumitem}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Abhinav Bhatia} \\ \vspace{1pt}
    \small Ph.D. student at University of Massachusetts Amherst $|$ \href{mailto:abhinavbhati@cs.umass.edu}{\underline{abhinavbhati@cs.umass.edu}} $|$ \href{https://abhinavbhatia.me}{\underline{abhinavbhatia.me}} 
    
    \begin{tiny}Last updated: Jan 30, 2026. Latest CV available at \href{https://abhinavbhatia.me/#cv}{abhinavbhatia.me/\#cv}\end{tiny}
   \end{center}


%-----------EDUCATION-----------

\section{Interests}
    Artificial Intelligence, Reinforcement Learning, Inverse RL, Meta RL, AI Safety, Real-time Planning, Robotics

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Massachusetts Amherst}{3.95/4}
      {MS/Ph.D. in Computer Science, advised by Prof. Shlomo Zilberstein}{Fall 2019 -- Present}
    \resumeSubheading
      {Birla Institute of Technology and Science (BITS) - Pilani, Pilani Campus}{9.27/10}
      {B.E. (Hons.) in Computer Science}{Aug. 2011 -- May 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Applied Sciences Intern}{June 2024 -- August 2024}
      {Xbox Game Studios, Microsoft}{Redmond, WA, USA}
      \resumeItemListStart
      \resumeItem{Used multi-task inverse reinforcement learning and offline reinforcement learning for automated game playing.}
      \resumeItemListEnd
    \resumeSubheading
      {Research Engineer}{June 2017 -- July 2019}
      {School of Computing and Information Sciences, Singapore Management University}{Singapore}
      \resumeItemListStart
          \resumeItem{Supervised by Prof. Pradeep Varakantham and Prof. Akshat Kumar.}
          \resumeItem{Worked on optimizing constrained resource allocation at city scale using deep reinforcement learning, which led to a publication at \emph{International Conference on Automated Planning and Scheduling (ICAPS) 2019}.}
        \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{August 2015 -- June 2017}
      {WalmartLabs}{Bengaluru, India}
      \resumeItemListStart
            \resumeItem{Was part of \emph{Operations, Analytics \& Research} team for supply-chain division of Walmart’s eCommerce.}
            \resumeItem{Developed an Elasticsearch based distributed database for data analysis.}
            \resumeItem{Developed a deep-learning based system for anomaly-detection in large live incoming data streams.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Development Engineering Intern}{January 2015 -- June 2015}
      {Amazon}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Worked on offline experience for Prime Video.}
        \resumeItem{Worked on optimizing content load time for Prime Video on Kindle tablets.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%------------SELECTED PUBLICTIONS---------
\section{Publications}

\textbf{Abhinav Bhatia}, Samer B. Nashed and Shlomo Zilberstein. ``RL$^3$: Boosting Meta Reinforcement Learning via RL inside RL$^2$". In \textit{NeurIPS Workshop on Generalization in Planning (NeurIPS GenPlan 2023)}, In \textit{Reinforcement Learning Conference (RLC 2025)} \\
\vspace{2mm}

Samer B. Nashed, Justin Svegliato, \textbf{Abhinav Bhatia}, Stuart Russell and Shlomo Zilberstein (2022). ``Selecting the partial state abstractions of MDPs: A metareasoning approach with deep reinforcement learning". In \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2022)}. \\
\vspace{2mm}

\textbf{Abhinav Bhatia}, Justin Svegliato, Samer B. Nashed and Shlomo Zilberstein. ``Tuning the Hyperparameters of Anytime Planning: A Metareasoning Approach with Deep Reinforcement Learning". In \textit{Proceedings of the International Conference on Automated Planning and Scheduling (ICAPS 2022)}.\\ 
\vspace{2mm}

\textbf{Abhinav Bhatia}, Philip S. Thomas, and Shlomo Zilberstein. ``Adaptive Rollout Length for Model-Based RL Using Model-Free Deep RL". In \textit{(ArXiv 2022)}.\\ 
\vspace{2mm}

\textbf{Abhinav Bhatia}, Justin Svegliato and Shlomo Zilberstein. ``On the Benefits of Randomly Adjusting Anytime Weighted A*". In \textit{Proceedings of the International Symposium on Combinatorial Search (SoCS 2021)}.\\ 
\vspace{2mm}

\textbf{Abhinav Bhatia}, Justin Svegliato and Shlomo Zilberstein. ``Tuning the Hyperparameters of Anytime Planning: A Deep Reinforcement Learning Approach". In \textit{ICAPS Workshop on Heuristics and Search for Domain-independent Planning (ICAPS HSDIP 2021)}.\\
\vspace{2mm}

\textbf{Abhinav Bhatia}, Pradeep Varakantham and Akshat Kumar. ``Resource Constrained Deep Reinforcement Learning". In \textit{Proceedings of the International Conference on Automated Planning and Scheduling (ICAPS 2019)}.\\ 
\vspace{2mm}


%-----------TEACHING EXPERIENCE-----------
\section{Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CS383 Artificial Intelligence}{UMass Amherst}
      {Responsible for designing quizzes, clarifying students' doubts and holding office hours}{Fall 2022}
  \resumeSubHeadingListEnd

%-----------HONORS-----------------------
\section{Misc.}
\begin{itemize}[noitemsep]
  \item Program Committee member, IJCAI 2026.
    \item Dissertation Writing Fellowship Award, UMass Amherst, Spring 2026.
    \item Program Committee member, IJCAI 2025.
    \item Organizing Committee member, AAAI 2025 GenPlan workshop.
    \item Program Committee member, IJCAI 2024.
    \item Program Committee member, NeurIPS 2023 GenPlan workshop.
    \item Paper reviewer, JMLR, 2023.
    \item Program committee member, AAAI 2023.
    \item Paper reviewer, AIJ, 2021.
    \item As a member of IEEE BITS-Pilani chapter, conceptualized, developed and organized an AI bot making competition for a video game at college tech festival 2014.
    \item Won 1st prize for project \emph{PC 3D Gesture Interface using Kinect} in design appliances category at BITS-Pilani tech festival 2014.
    \item Offered \emph{Kishore Vaigyanik Protsahan Yojana} fellowship, which is an initiative by govt. of India to encourage young students to pursue a career science research, 2010.
\end{itemize}

\section{Programming Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Experienced in C, Python, Julia, C++, Java. Familiar with C\#, SQL} \\
     \textbf{Frameworks}{: OpenAI Gym, PyTorch, FluxML, Tensorflow, CPLEX, Elasticsearch, Unity3D}
    }}
 \end{itemize}

\section{Relevant Ph.D. coursework}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Artificial Intelligence, Reinforcement Learning, Robotics, Advanced Robot Dynamics \& Control, Machine Learning, Neural Networks, Advanced Algorithms, Empirical Research Methods
    }}
 \end{itemize}

\section{Links}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Webpage}{: \href{https://abhinavbhatia.me}{https://abhinavbhatia.me} \\
     \textbf{Github}{: \href{https://github.com/bhatiaabhinav}{https://github.com/bhatiaabhinav}} \\
     \textbf{Google Scholar}{: \href{https://scholar.google.com/citations?user=Y53CNrIAAAAJ\&hl}{https://scholar.google.com/citations?user=Y53CNrIAAAAJ\&hl}} 
    }}}
 \end{itemize}
 
\section{Contact Information}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Email}{: \href{mailto:abhinavbhati@cs.umass.edu; abhinav.bhatia.me@gmail.com}{abhinavbhati@cs.umass.edu; abhinav.bhatia.me@gmail.com}} \\
    }}
 \end{itemize}




%-------------------------------------------
\end{document}
